Revenue Maximization for Buyers with Costly Participation

### 2025-03-19 paper/paper.tex
Increase node sizes
Without loss

 Since we focus on revenue maximization, it is w.l.o.g. to consider $p_0 \geq 0$ \cite{primary}.
 Further \citet{primary} showed that for any mechanism with $p_0 \geq 0$ there exists a mechanism with weakly higher revenue that has $p_0 = 0$.
 Therefore, from now on, we disregard $p_0$.

@@

 \begin{figure}[htp!]
     \centering
     \begin{tikzpicture}[
             node/.style={circle, draw=black, fill=gray!20, scale=.3},
             axis/.style={->, thick},
             gridline/.style={gray, dashed}
         ]

>>>>

 From \citet{primary} showed that for any mechanism with $p_0 \neq 0$ there exists a mechanism with weakly higher revenue that has $p_0 = 0$.
 Therefore, from now on, we disregard $p_0$.

@@

 \begin{figure}[htp!]
     \centering
     \begin{tikzpicture}[
             node/.style={circle, draw=black, fill=gray!20, scale=.35},
             axis/.style={->, thick},
             gridline/.style={gray, dashed}
         ]
